Sexual selection improves population fitness: a meta-analysis

### 2018-09-19 Manuscripts/Manuscript_MetaAnalysis.Rmd
Figure 3 Caption Update (was empty before)

\newpage
```{r, echo = F, warning=F, message = F}
library(knitr)
library(kableExtra)
library(dplyr)

```

@@

```{r, echo = FALSE, fig.cap="Tests of publication bias are mixed and suggest publication bias may be present. (**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies. (**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias. For (**b**) and (**c**) circle size is proportional to the weight (%) of the study, which is inversely proportional to the variance of the effect size."}
knitr::include_graphics("Figures/publicationbias.pdf") #Not relative path
```
\newpage

>>>>

\newpage
```{r, echo = F, warning=F, message = F}
library(knitr)
library(kableExtra)
library(dplyr)
```

@@

```{r, echo = FALSE, fig.cap= "Tests of publication bias are mixed and suggest publication bias may be present. (**a**) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies. (**b**) No significant correlation exists between journal impact factor and effect size, (**c**) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias. For (**b**) and (**c**) circle size is proportional to the weight (%) of the study, which is inversely proportional to the variance of the effect size."}
knitr::include_graphics("Figures/publicationbias.pdf") #Not relative path
```

<!-- Appears to be a problem having two captions -->
\newpage
